### 2014-05-09 tex/main-body-text.tex
Revised figures added
Added references, made some slight changes to results section

\section*{Results}

\subsection*{{\sc flock} analysis of coasta California steelhead} 
{\sc flock} was run four times using the default setting for all run parameters 
\textit{(initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0)} for values of \textit{k} from 2 to 6. The stopping point of 
\textit{k}=6 was chosen because four consecutive runs with 0 length plateaus were 
produced. 
Run times were relatively short. The four groups of runs for the default settings 
averaged 217 minutes (30min SD) on an i7 3.40GHz processor with 8GB of RAM. While no 
plateaus were observed in any of the four groups for a \textit{k} greater than two, 
the plateau record varied greatly among each group for \textit{k}=2 (plateau 
sequences- Run1=3,2,5,6,3; Run2=2,2,2,4,3,2; Run3=2,3,2,4; and Run4=2,3,3,4,2,2,5,2). 
The plateau analysis procedure suggested by \citet{Duc&Tur2012} leads to two different 
conclusions for the plateau sequences observed: \textit{k}=2 is the lower bound 
estimate (Run1) or there is no estimate (\textit{undecided}: Runs 2-4). Despite 
different conclusions, the allocation of individuals for the 'best run' from each 
group differed by a only a single individual. When \textit{k}=2, {\sc flock} 
identifies a boundary in the Russian Gulch area clustering individuals into northern 
and southern groups (Fig. 1).

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{images/Figures-Pat/FLOCK_OneSampDefault.pdf}
    \caption{Assignment to reference population (from \textit{k} = 2-6) plots created 
in the program {\sc flock}. Each horizontal plot represents the 'best run' from a 
series where individuals are reallocated into \textit{k} clusters. Within each plot 
the normalized individual likelihood for each reference population is represented by a 
colored vertical bar. Major geographic boundaries that were attributed to genetic 
structure in \citet{Garzaetal_norcal} are indicated with black vertical lines. Results 
from the 'best runs' showed similar geographic differentiation to 
\citet{Garzaetal_norcal} analysis. The plateau analysis developed by 
\citet{Duc&Tur2012} indicate that either an undecided structure or that \textit{k}=2 
is the lower bound estimate.}
    \label{Fig.1}
\end{center}
\end{figure*}

>>>>

\section*{Performance Comparison with {\sc structure}}

\subsection*{Analysis of coasta California steelhead} 
To evaluate the preformance and computational efficiency of {\sc flock}  we used a published 
dataset from \citet{Garzaetal_norcal} comprised of 2596 steelhead \textit{Oncorhynchus mykiss}
genotyped at 15 microsatellite loci.  {\sc flock} was run six times using the default setting for all run parameters 
\textit{(initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0)} for values of \textit{k} from 2 to 6. The stopping point of 
\textit{k}=6 was chosen because four consecutive runs with 0 length plateaus were 
produced. The non-admixture, uncorrelated allele frequency model implemented in {\sc structure}
was run with six iterations of a 50,000 sweep burn-in followed by 150,000 sweep sample 
from the posterior of \textit{k} from 2 to 6. To facilitate the comparison of the two programs,
the program {\sc clump} \citep{Jak&Ros2007} was used to relabel clusters among different runs,
while the program Distruct \citep{Rosenberg2004} was used to plot individual \textit{$q_i$} values.

\subsection*{Results} 
Run times were relatively short. The four groups of runs for the default settings 
averaged 217 minutes (30min SD) on an i7 3.40GHz processor with 8GB of RAM. While no 
plateaus were observed in any of the four groups for a \textit{k} greater than two, 
the plateau record varied greatly among each group for \textit{k}=2 (plateau 
sequences- Run1=3,2,5,6,3; Run2=2,2,2,4,3,2; Run3=2,3,2,4; and Run4=2,3,3,4,2,2,5,2). 
The plateau analysis procedure suggested by \citet{Duc&Tur2012} leads to two different 
conclusions for the plateau sequences observed: \textit{k}=2 is the lower bound 
estimate (Run1) or there is no estimate (\textit{undecided}: Runs 2-4). Despite 
different conclusions, the allocation of individuals for the 'best run' from each 
group differed by a only a single individual. When \textit{k}=2, {\sc flock} 
identifies a boundary in the Russian Gulch area clustering individuals into northern 
and southern groups (Fig. 1).

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{images/Figures-Pat/Flock-Fig1.pdf}
    \caption{Assignment to reference population (from \textit{k} = 2-6) plots created 
in the program {\sc flock}. Each horizontal plot represents the 'best run' from a 
series where individuals are reallocated into \textit{k} clusters. Within each plot 
the normalized individual likelihood for each reference population is represented by a 
colored vertical bar. Major geographic boundaries that were attributed to genetic 
structure in \citet{Garzaetal_norcal} are indicated with black vertical lines. Results 
from the 'best runs' showed similar geographic differentiation to 
\citet{Garzaetal_norcal} analysis. The plateau analysis developed by 
\citet{Duc&Tur2012} indicate that either an undecided structure or that \textit{k}=2 
is the lower bound estimate.}
    \label{Fig.1}
\end{center}
\end{figure*}
